### 2015-06-14 writing/S'15 LSTM/discussion.tex
Text summary of learning curve

The results are shown in Figure \ref{prop-results}\todo{Next version of figures will have vertical dividing lines at 3,4,6}. All four models were able to largely memorize the training data (TODO, TODO, TODO, and TODO for $\le$6). In the $\le$6 setting, the three tree models were able to perform at above TODO\% on examples of size $\le$2 with a steady decay in performance continuing through TODO\% at size 12, and similar, if steeper, decays with smaller training sets. All four robustly beat the simple baselines reported in Bowman et al.: the most frequent class occurs just over 50\% of the time, and a summing model that ignores word order does reasonably on the shortest examples but falls below 60\% by bin 4.

@@

[Something about the learning curve that doesn't involve a figure. Something about the learning curve that doesn't involve a figure. Something about the learning curve that doesn't involve a figure.]

>>>>

The results are shown in Figure \ref{prop-results}\todo{Next version of figures will have vertical dividing lines at 3,4,6}. All four models were able to largely memorize the training data (TODO, TODO, TODO, and TODO for $\le$6, pooling across bins). In the $\le$6 setting, the three tree models were able to perform at above TODO\% on examples of size $\le$2 with a steady decay in performance continuing through TODO\% at size 12, and similar, if steeper, decays with smaller training sets. All four robustly beat the simple baselines reported in Bowman et al.: the most frequent class occurs just over 50\% of the time, and a summing model that ignores word order does reasonably on the shortest examples but falls below 60\% by bin 4.

@@

Learning curve experiments suggest that none of these models are saturated, and that still larger data sets could help even on this simple task. The LSTM in the $\le6$ strikingly moves from TODO\% accuracy with a random 33\% of the available training data to TODO\% on all of it. The plain TreeRNN shows the smallest improvement, moving from TODO\% to TODO\%.
